\section{The Leximax Universal-Regret core}
\label{sec:core}

Figure~\ref{fig:pipeline} gives the end-to-end view of the rule developed in this
section: from a candidate set, through normalisation and the declared probe family,
to the leximax selection and its certificate.

\input{tikz/fig_pipeline}

\subsection{Problem setting and normalisation}
Let $\X\subseteq\R^n$ be the feasible set and $F:\X\to\R^m$, $F(x)=(f_1(x),\dots,
f_m(x))$, the vector objective.

\begin{center}
\fbox{
\begin{minipage}{0.9\columnwidth}
\textbf{Convention:} All criteria $f_i$ are assumed to be \emph{minimised}. Maximisation objectives must have their sign reversed before normalisation. Consequently, lower normalised values $r_i$ are better, and probes are non-decreasing functions of these costs.
\end{minipage}
}
\end{center}

For
the finite case let $A=\{x_1,\dots,x_N\}\subseteq\X$ be a candidate set, e.g.\ an
\emph{a posteriori} approximation of the efficient set. Before evaluation, Pareto-dominated alternatives are removed from $A$ unless the analyst explicitly requires selection over the raw un-filtered set. For the continuous case (\S\ref{sec:direct}) $A$ is not required. Criteria are normalised to $[0,1]$ by the
positive affine map
\begin{equation}
r_i(x)=\frac{f_i(x)-\ideal_i}{\nadir_i-\ideal_i},\qquad
\ideal_i=\min_{x\in A}f_i(x),\;\; \nadir_i=\max_{x\in A}f_i(x),
\label{eq:norm}
\end{equation}
which attains both endpoints on $A$. A criterion is flagged as numerically degenerate if the range $\nadir_i-\ideal_i$ approaches zero. Degenerate criteria are reported and excluded from non-singleton probe construction unless the analyst supplies external bounds. If a criterion is degenerate over $A$, strict Pareto improvement on that criterion cannot occur inside $A$. If external bounds are supplied, singleton probes for degenerate criteria can remain. Excluding degenerate criteria does not weaken the strict Pareto compatibility for the remaining non-degenerate dimensions.

For the finite case all extrema ($\ideal$,
$\nadir$, $q^\star$, $q^{\mathrm w}$ below) are taken over the active candidate set $A$;
We use the active-set maximum over $A$, not the true nadir. It is a valid upper endpoint for the evaluated candidate set, but not necessarily a conservative bound for the underlying feasible problem unless $A$ is known to contain the relevant nadir-attaining efficient points or external bounds are supplied. The rule is invariant to
positive affine rescaling of the criteria when the bounds are transformed
consistently; it is not invariant to arbitrary monotone transformations (e.g.\
$f_i\mapsto\log f_i$), which change the distances that define regret---so such
transformations are a modelling choice the analyst must make deliberately. Because LexUR uses active-set normalisation, its recommendation is strongly set-dependent: adding a non-selected extreme candidate can change the normalisation and thus the recommendation. Consequently, LexUR is recommended only when the normalisation bounds are either fixed externally or reported through an interval/stability analysis.

\subsection{Admissible probes}
A \emph{probe} is a scalar function $q:[0,1]^m\to\R$ encoding a rational decision
question. The family $\Q$ is \emph{declared}: it is part of the specification.

\begin{definition}[Admissible probe]
\label{def:probe}
A probe $q$ is \emph{admissible} if (i) it is non-decreasing in each $r_i$
(monotonicity) and (ii) $q(\mathbf 1)>q(\mathbf 0)$, so it can be rescaled such that $q(\mathbf 0)=0$ and $q(\mathbf
1)=1$ (normalisation).
\end{definition}

Here $\mathbf 0$ and $\mathbf 1$ denote the all-zeros and all-ones vectors. The initial endpoint normalisation ($q(\mathbf 0)=0, q(\mathbf 1)=1$) serves to make values structurally scale-comparable across the heterogeneous family, before the empirical disappointment anchors ($q^\star, q^{\mathrm w}$) re-normalise the observed active range.
Monotonicity gives \emph{weak} Pareto compatibility; strict compatibility needs a
separation property (Definition~\ref{def:sep}). Canonical admissible probes are
the \emph{singletons} $q_i(r)=r_i$; the \emph{grand mean} $q_\mu(r)=\frac1m
\sum_i r_i$ (the utilitarian question); the \emph{grand maximum}
$q_{\max}(r)=\max_i r_i$ (the egalitarian/worst-criterion question); and, for any
coalition $S\subseteq\{1,\dots,m\}$, the coalition mean and maximum. All have
non-negative weights or are maxima, hence are monotone.

\begin{definition}[Separating family]
\label{def:sep}
A probe family $\Q$ \emph{separates} criteria if for every $i$ there is a probe
$q\in\Q$ strictly increasing in $r_i$. Including all $m$ singleton probes
$q_i(r)=r_i$ is sufficient; LexUR always does so.
\end{definition}

\begin{remark}[Probe multiplicity is a modelling choice]
\label{rem:multiplicity}
The probe family is treated as a \emph{deduplicated labelled set}: each declared
question appears once. Duplicating a probe is \emph{not} neutral. Because the
leximax order sorts the full vector of probe-wise disappointments, a repeated
probe contributes its disappointment more than once to the sorted vector and can
therefore change lower-order lexicographic tie-breaking and the labelled
certificate. Probe multiplicities thus act as implicit importance weights and
must be interpreted as deliberate modelling choices, not as a harmless
restatement of the same question. (The singleton probes are retained once each
for separation, Definition~\ref{def:sep}.)
\end{remark}

\subsection{Disappointment and regret}
For each probe $q\in\Q$ let $q^\star=\min_{x\in A}q(r(x))$ and $q^{\mathrm w}=\max_{x\in A}q(r(x))$
(or a user-supplied worst-acceptable bound, subject to $q^{\mathrm w}\ge\max_{x\in A}q(r(x))$ and $q^{\mathrm w}-q^\star\ge\varepsilon_q$). Define the active range $R_q = q^{\mathrm w} - q^\star$. If $R_q < \varepsilon_q$ for a small numerical threshold, the probe is degenerate and is excluded from the primary decision vector. Otherwise, the \emph{normalised disappointment} of $x$ under $q$ is
\begin{equation}
\reg_q(x)=\frac{q(r(x))-q^\star}{R_q}\in[0,1],
\label{eq:disap}
\end{equation}
so that $\reg_q(x)=0$ iff $x$ is $q$-optimal and $1$ iff $x$ attains the worst bound.

We use the term \emph{disappointment} for the normalised shortfall of an alternative from the best attainable value of a single given probe, and \emph{regret certificate} for the vector collecting these probe-wise disappointments. This is regret-like but differs from classical pairwise Savage regret unless the probe family is interpreted specifically as the uncertainty set of possible true preference functions.

\subsection{The leximax order}
Collect $\reg(x)=(\reg_{q_1}(x),\dots,\reg_{q_K}(x))$, $K=|\Q|$, and sort it in
\emph{descending} order to obtain $\reg^{\downarrow}(x)=(\reg_{[1]}(x)\ge\dots\ge
\reg_{[K]}(x))$. The \textbf{Leximax Universal-Regret order}, a lexicographic minimax regret rule, is
\begin{equation}
x\preceq_{\mathrm{LexUR}}y \iff \reg^{\downarrow}(x)\lex \reg^{\downarrow}(y),
\label{eq:lexur}
\end{equation}
i.e.\ $x$ is preferred if its worst disappointment is smaller; on ties, its
second worst; and so on. We use the term \emph{lexicographic minimax regret}
(equivalently \emph{leximax} of the sorted disappointments) consistently; this is
exactly leximin applied to the negated disappointments, so the ``leximax'' and
``leximin'' descriptions coincide and we adopt the minimax-regret reading
throughout. The \emph{LexUR solution} is $x^{\mathrm{LexUR}}\in
\argmin^{\mathrm{lex}}_{x}\reg^{\downarrow}(x)$, and its \emph{certificate} is the
labelled, sorted vector $\reg^{\downarrow}(x^{\mathrm{LexUR}})$ together with the
probes attaining the largest entries. Figure~\ref{fig:leximax} illustrates the
comparison on a two-alternative example.

\input{tikz/fig_leximax}

Exact LexUR defines a complete preorder, and we write $W_0=\argmin^{\mathrm{lex}}_{x\in A}\reg^{\downarrow}(x)$ for its set of exact minimisers. In computation and practical reporting, a tolerance $\tau>0$ is used to absorb estimation noise. For sorted vectors $a,b\in[0,1]^K$, define $a\prec_\tau b$ if there exists $k=\min\{j: |a_j-b_j|>\tau\}$ and $a_k<b_k-\tau$. The $\tau$-tolerance set is then
\[ W_\tau=\{x\in A:\nexists\, y\in A \text{ such that } \reg^{\downarrow}(y)\prec_\tau \reg^{\downarrow}(x)\}. \]
We stress the precise status of these objects. $W_\tau$ is the set of $\tau$-\emph{undominated} alternatives under the relation $\prec_\tau$, which is irreflexive but \emph{not} transitive; hence $\prec_\tau$ is neither a preorder nor does it induce an equivalence relation, and $W_\tau$ is \emph{not} an equivalence class. We therefore avoid the terms ``tolerance class'' and ``indifference class'' for $W_\tau$. When a uniquely stable recommendation is wanted, the appropriate object is the numerical stability set around an exact winner $x^\star\in W_0$, namely $C_\tau(x^\star)=\{x\in A:\reg^{\downarrow}(x)\not\succ_\tau \reg^{\downarrow}(x^\star)\}$ (the alternatives not significantly worse than $x^\star$ under the declared tolerance), whose singleton-ness is guaranteed only under the margin condition of Theorem~\ref{thm:stab}. The $\tau$-tolerance rule is thus a numerical reporting and stability device around the exact or margin-separated winner, not a substitute preorder.

\subsection{Interval bounds and the stability set}
Because point estimates of normalisation bounds can cause frequent winner flips, true robustness requires evaluating the regrets over conservative interval bounds. We take $\mathcal B$ to be a genuinely \emph{bounded} uncertainty box: each lower bound ranges in an interval $z_i^{\star,b}\in[\underline z_i^{\star},\overline z_i^{\star}]$ and each upper bound in $z_i^{nad,b}\in[\underline z_i^{nad},\overline z_i^{nad}]$, with the containment and range conditions
\[
\overline z_i^{\star}\le \min_{x\in A} f_i(x),\qquad \underline z_i^{nad}\ge \max_{x\in A} f_i(x),\qquad z_i^{nad,b}-z_i^{\star,b}\ge \delta_i>0\quad\forall i,
\]
so that
\[
\mathcal{B} = \Big\{b=(z^{\star,b},z^{nad,b}) :\ z_i^{\star,b}\in[\underline z_i^{\star},\overline z_i^{\star}],\ \ z_i^{nad,b}\in[\underline z_i^{nad},\overline z_i^{nad}]\ \ \forall i\Big\}
\]
is a compact box. Boundedness guarantees that the suprema defining the worst-case envelope (Option C) are attained and finite. The containment conditions $\overline z_i^{\star}\le\min_A f_i$ and $\underline z_i^{nad}\ge\max_A f_i$ are required so that every normalised value
\[ r_i^b(x)=\frac{f_i(x)-z_i^{\star,b}}{z_i^{nad,b}-z_i^{\star,b}} \]
remains in $[0,1]$ for all $x\in A$, which is the domain on which the probes $q:[0,1]^m\to\R$ are defined; the positive-range floor $\delta_i$ keeps the map well defined. (If one wishes to admit bounds that do not contain the active range, the domain of every $q$ must be extended beyond $[0,1]^m$ explicitly.) For each bound scenario $b \in \mathcal{B}$ one then computes the disappointment $\reg_q^b(x)$, the sorted vector $\reg^{b,\downarrow}(x)$, and the $\tau$-undominated set $W_\tau(b)$ as defined above.

The robust framework defines two fundamental stability sets:
\begin{enumerate}
    \item \textbf{Necessary interval winner (Option A):} The intersection across all bounds:
    \[ S_{\text{necessary}}^\tau=\bigcap_{b\in\mathcal B} W_\tau(b). \]
    \item \textbf{Possible interval winner (Option B):} The set of alternatives that win under some plausible bound:
    \[ S_{\text{possible}}^\tau=\bigcup_{b\in\mathcal B} W_\tau(b). \]
\end{enumerate}
The necessary set is always a subset of the possible set. A unique robust recommendation exists if $W_\tau(b)=\{x^\star\}$ for all $b\in\mathcal B$. A uniform positive margin over $\mathcal B$ (Theorem~\ref{thm:stab} holding at every $b$) is a \emph{sufficient} certificate of this property, but it is \emph{not} necessary: the intersection $S_{\text{necessary}}^\tau=\bigcap_b W_\tau(b)$ can be a singleton even when some $W_\tau(b)$ contain extra alternatives and no uniform margin holds, and conversely a singleton necessary set does not by itself guarantee a unique recommendation across all bounds. When the necessary set is empty or the possible set contains several alternatives, the output should be reported as a stability set rather than a unique recommendation (and, per the remarks on $W_\tau$ above, not as an equivalence or indifference class).

For a single-shot operational robust default (Option C), one can compute the worst-case robust certificate:
\[ \overline \reg_q(x) = \sup_{b \in \mathcal{B}} \reg^b_q(x), \]
and then select the recommendation by lexicographic minimisation of the sorted worst-case regrets $\overline \reg^{\downarrow}(x)$. Because the supremum is taken \emph{separately} for each probe $q$, $\overline\reg(x)$ is a componentwise conservative envelope: its coordinates may be attained under different bound scenarios and need not be jointly realised under any single $b\in\mathcal B$. This worst-case robust default is a \emph{separate}, conservative selection rule: its minimiser need \emph{not} belong to the possible-winner set $S_{\text{possible}}^\tau$, and it should therefore be reported alongside the necessary and possible interval-winner sets rather than interpreted as an element of them. This is the familiar robust-optimisation phenomenon that a minimax compromise can be optimal under no individual scenario. For example, with a single probe and two bound scenarios $b_1,b_2$ giving disappointments $(\reg^{b_1},\reg^{b_2})$ of $A{=}(0,1)$, $B{=}(1,0)$ and $C{=}(0.4,0.4)$, we have $S_{\text{possible}}^\tau=\{A,B\}$, yet $\overline\reg(A)=\overline\reg(B)=1>\overline\reg(C)=0.4$, so the robust default selects $C\notin S_{\text{possible}}^\tau$.

\subsection{Foundational guarantees}
\begin{theorem}[Existence and completeness of exact LexUR]
\label{thm:exist}
For any finite $A$ and finite $\Q$, $x^{\mathrm{LexUR}}$ exists and exact
$\preceq_{\mathrm{LexUR}}$ is a complete preorder on $A$.
\end{theorem}
\begin{proof}
For finite $A$ and finite $\Q$, each $\reg^{\downarrow}(x)\in[0,1]^K$ is a
well-defined real vector. The lexicographic order on $\R^K$ is reflexive,
transitive and total, hence a complete preorder; since $A$ is finite the
lexicographic minimum exists.
\end{proof}

\begin{theorem}[Weak and strict Pareto compatibility]
\label{thm:pareto}
Let $x$ strictly Pareto-dominate $y$ and let every $q\in\Q$ be monotone
non-decreasing in each $r_i$. Then $\reg_q(x)\le\reg_q(y)$ for all $q$
(\emph{weak} compatibility), so $x\preceq_{\mathrm{LexUR}}y$. If, in addition, $\Q$
\emph{separates} criteria (Definition~\ref{def:sep})---in particular if $\Q$
contains the singleton probes---then $\reg_q(x)<\reg_q(y)$ for some $q$ and
$x\prec_{\mathrm{LexUR}}y$.
\end{theorem}
\begin{proof}
Let $x\prec_P y$, so $r_i(x)\le r_i(y)$ for all $i$ with strict inequality for
some $j$. For any monotone non-decreasing probe $q$, $q(r(x))\le q(r(y))$; as
$q^\star,q^{\mathrm w}$ are constants independent of the alternative,
$\reg_q(x)\le\reg_q(y)$ for every $q\in\Q$. We now invoke the monotonicity of
order statistics: if $a_q\le b_q$ for every probe $q$, then the descending
rearrangements satisfy $a^{\downarrow}_k\le b^{\downarrow}_k$ for all $k$ (the
$k$-th largest of a componentwise-smaller vector cannot exceed the $k$-th largest
of the larger one). Applying this to $a_q=\reg_q(x)$ and $b_q=\reg_q(y)$ gives
$\reg^{\downarrow}_k(x)\le\reg^{\downarrow}_k(y)$ for all $k$, hence
$x\preceq_{\mathrm{LexUR}}y$ (weak compatibility, monotonicity only). If $\Q$
separates criteria there is a probe $q$ strictly increasing in $r_j$; provided
this separating probe is non-degenerate over $A$ (active range $q^{\mathrm
w}-q^\star\ge\varepsilon_q>0$, which holds automatically whenever $q$ strictly
separates two alternatives of $A$), $q(r(x))<q(r(y))$ gives $\reg_q(x)<\reg_q(y)$.
The disappointment vector of $x$ is then componentwise $\le$ that of $y$ with at
least one strict drop, so by the same order-statistic monotonicity (now with one
strict inequality) the descending-sorted vectors satisfy
$\reg^{\downarrow}(x)\lex\reg^{\downarrow}(y)$ strictly and
$x\prec_{\mathrm{LexUR}}y$. The counterexample in the main text shows the
separation hypothesis cannot be dropped.
\end{proof}

The separation hypothesis is necessary: with only the probe $q(r)=r_2$, the
dominator $r(x)=(0,1)$ and the dominated $r(y)=(0.1,1)$ have equal disappointment,
so monotonicity alone does not give a strict preference. LexUR always includes the
singletons, so it separates.

\begin{corollary}[Dominated exclusion]
\label{cor:dom}
Let $A$ be the active candidate set. If $x \in A$ is Pareto-dominated by some $y \in A$, and $\Q$ separates criteria, then
$x$ is not LexUR-optimal over $A$.
\end{corollary}
\begin{proof}
If $x \in A$ is dominated by some $y \in A$ and $\Q$ separates criteria,
Theorem~\ref{thm:pareto} gives $y\prec_{\mathrm{LexUR}}x$, so $x$ is not a
lexicographic minimiser over $A$. Without separation only $y\preceq_{\mathrm{LexUR}}x$ holds
and a dominated alternative may tie its dominator.
\end{proof}

\begin{theorem}[Stability of the implemented winner under a margin condition]
\label{thm:stab}
Let $\hat\reg_q(x)$ estimate $\reg_q(x)$
with $\eta=\max_{x,q}|\hat\reg_q(x)-\reg_q(x)|$. Suppose the exact winner
$x^{\mathrm{LexUR}}$ beats every rival $y$ at the first coordinate $k(y)$ at which
their sorted vectors differ by more than $\tau$, with margin
$\reg_{[k(y)]}(y)-\reg_{[k(y)]}(x^{\mathrm{LexUR}})\ge\Delta$, and that all earlier
coordinates agree within $\tau-2\eta$. If $2\eta<\min\{\Delta-\tau,\ \tau\}$, the
winner under $\hat\reg$ is unchanged.
\end{theorem}
\begin{proof}
Write $\hat\reg_q(x)=\reg_q(x)+\xi_q(x)$, $|\xi_q(x)|\le\eta$; sorting is
$1$-Lipschitz in $\|\cdot\|_\infty$, so each sorted coordinate moves by at most
$\eta$. Fix a rival $y$ and the deciding coordinate $k=k(y)$ with true margin
$\reg_{[k]}(y)-\reg_{[k]}(x^{\mathrm{LexUR}})\ge\Delta$. Under perturbation this
margin is at least $\Delta-2\eta$; since $2\eta<\Delta-\tau$ it stays above
$\tau$, so the $\tau$-tolerance rule still decides coordinate $k$ in favour of
$x^{\mathrm{LexUR}}$. For the earlier coordinates $j<k$, which agree within
$\tau-2\eta$ by hypothesis, the perturbed gaps stay within $\tau$ and are treated
as ties, so the decision is not pre-empted before $k$. As $2\eta<\tau$ no spurious
strict difference is created earlier. Hence $x^{\mathrm{LexUR}}$ still beats every
rival and the winner is unchanged. (Exact comparison, $\tau=0$, is excluded
precisely because the second condition $2\eta<\tau$ then fails.)
\end{proof}

Theorem~\ref{thm:stab} is deliberately stated for the tolerance rule: exact
lexicographic comparison is \emph{not} perturbation-stable, because a winner that
beats a rival only at a later coordinate after an exact earlier tie can be
reversed by an arbitrarily small perturbation of the earlier coordinate. The
tolerance $\tau$ absorbs exactly those near-ties. We
note that the margin condition $\Delta$ in Theorem~\ref{thm:stab} can be
restrictive on densely packed candidate sets, where the separation between
certificates may be very small. Without that margin the theorem gives no winner
stability guarantee; the appropriate output is therefore a tolerance or
stability set rather than a uniquely stable recommendation. For
continuous $\X$, existence requires compactness of $\X$ and continuity of each
$q\circ r$; uniqueness is not guaranteed and a small set of tied exact minimisers may arise.

