\section{Held-out preference families and broadened-protocol specification}
\label{app:families}

This appendix gives the formal specification of the held-out evaluation families
and the broadened audit protocol of \S\ref{sec:protocol}, for reproducibility.
None of these families is used to construct LexUR probes. they exist only to score
recommendations out of class.

\paragraph{Notation and scoring.}
Let $r(x)\in[0,1]^m$ be the active-set normalised criterion vector of alternative
$x$ (minimisation, lower is better). Each family produces, for $T$ sampled
parameterisations, a utility $u(\cdot)$ (higher is better). a recommendation is
scored by the held-out loss of Eq.~\eqref{eq:heldoutloss},
$L_u(x)=\bigl(u(x^\star_u)-u(x)\bigr)/\bigl(u(x^\star_u)-u(x^-_u)\bigr)$, with
$x^\star_u,x^-_u$ the in-sample best and worst alternatives for $u$ on $A$. Unless
stated otherwise, importance weights are drawn from a Dirichlet distribution
$w\sim\mathrm{Dir}(\alpha\mathbf 1)$, whose shape parameter $\alpha\in\{0.2,1,5\}$
yields sparse/extreme, uniform-simplex, and balanced preferences respectively.

\paragraph{The ten families.}
Writing $u(x)$ for the utility (higher better), the families are:
\begin{itemize}
\item \textbf{linear:} $u(x)=-w^\top r(x)$, $w\sim\mathrm{Dir}(\alpha\mathbf 1)$.
\item \textbf{sparse-linear:} as linear but only the $k=\lceil m/3\rceil$ largest
weights are kept and renormalised to sum to one (a DM attending to a few
criteria).
\item \textbf{Chebyshev:} $u(x)=-\max_i w_i r_i(x)$ (weighted Chebyshev / pure
ASF direction).
\item \textbf{augmented ASF:} $u(x)=-\bigl(\max_i w_i r_i(x)+0.05\,w^\top r(x)\bigr)$,
i.e.\ the Chebyshev term plus a small $\rho=0.05$ linear augmentation on the same
weights.
\item \textbf{$L_p$ compromise:} $u(x)=-\bigl(\sum_i w_i r_i(x)^p\bigr)^{1/p}$ with
exponent $p\sim\mathrm{Unif}(1.5,4.0)$ drawn per utility.
\item \textbf{CES:} $u(x)=-\bigl(\sum_i w_i r_i(x)^{\varrho}\bigr)^{1/\varrho}$ with
elasticity exponent $\varrho\sim\mathrm{Unif}(2.0,5.0)$ drawn per utility
(constant-elasticity-of-substitution disutility). We note plainly that the $L_p$
and CES families are \emph{intentionally adjacent} rather than independent: both
are norm-like disutilities of the same functional form, differing only in the
exponent range. Likewise Chebyshev and augmented ASF are near-identical by
construction (\S\ref{sec:exp}). We therefore do not claim ten \emph{independent}
preference geometries. the families are chosen to span a graded distance from the
probe family (in-class to adversarial), not to be mutually orthogonal.
\item \textbf{OWA:} $u(x)=-\sum_{k=1}^m \omega_k\, r_{[k]}(x)$, where $r_{[k]}$ is
the $k$-th largest normalised criterion and the ordered weights
$\omega=\mathrm{sort}^{\downarrow}\!\bigl(\mathrm{Dir}(\mathbf 1)\bigr)$ are a
descending-sorted uniform-simplex draw (emphasis on worst coordinates).
\item \textbf{Choquet-inspired ($2$-additive, max-interaction):}
$u(x)=-\bigl(a^\top r(x)+\sum_{i<j} b_{ij}\max(r_i(x),r_j(x))\bigr)$ with
non-negative masses $a_i\sim\mathrm{Unif}(0,1)$ on singletons and
$b_{ij}\sim\mathrm{Unif}(0,0.5)$ on pairs. This is a monotone non-additive
pairwise-interaction utility in the \emph{spirit} of a $2$-additive Choquet
integral. we deliberately avoid claiming it is exactly the standard $2$-additive
Choquet integral (whose Möbius/capacity form involves $\min$ terms for the
pairwise interactions), and use it only as a genuinely non-additive held-out
family.
\item \textbf{satisficing:} $u(x)=-\sum_i \max\bigl(r_i(x)-\vartheta_i,0\bigr)$ with
per-criterion aspiration thresholds $\vartheta_i\sim\mathrm{Unif}(0.2,0.6)$,
penalising only exceedances of the aspiration levels.
\item \textbf{max-min (group regret):} three stakeholder weight vectors
$w^{(1)},w^{(2)},w^{(3)}\sim\mathrm{Dir}(\alpha\mathbf 1)$ define
$u(x)=-\max_{s}\, (w^{(s)})^\top r(x)$, the worst-stakeholder linear disutility.
\end{itemize}
Families are grouped by distance from the probe family as \emph{in-class}
(linear, sparse-linear, Chebyshev, augmented ASF), \emph{adjacent}
($L_p$, CES, OWA), \emph{out-of-class} (Choquet, satisficing) and
\emph{adversarial} (max-min group regret). this scoping is fixed in the frozen
config.

\paragraph{Protocol grid.}
The broadened protocol of \S\ref{sec:protocol} sweeps candidate-set sizes
$N\in\{100,300,1000\}$, criteria $m\in\{3,5,8,10,15,20\}$, the eight geometries
(linear, convex, concave, disconnected, degenerate, asymmetric, many-knee,
irregular), and $50$ replications, for $3\times6\times8\times50=\protocolInstances{}$
paired instances. A Dirichlet shape $\alpha\in\{0.2,1,5\}$ is assigned to each
replication by deterministic cycling ($\alpha=\alpha_{\,\mathrm{rep}\bmod 3}$), so
the three shapes are nearly balanced ($17,17,16$ over the $50$ replications) within each $(N,m,\text{geometry})$ cell. The paired
non-inferiority confidence intervals (\S\ref{sec:protocol}) use a cluster
bootstrap with the instance keys as resampling units. The same candidate sets and held-out utility draws are shared across
all methods within an instance to ensure paired comparisons. All parameter
distributions above, the random seeds, and the frozen acceptance gates are fixed
in the released configuration file and reproduced by a single command.

\paragraph{Front geometries.}
Let $s$ denote a point drawn on the unit simplex (symmetric Dirichlet) and
$d$ a vector with $d_i=\sqrt{U_i}$, $U_i\sim\mathrm{Unif}(0,1)$. every set is then
reduced to its non-dominated subset. The eight geometries are:
\begin{itemize}
\item \textbf{linear:} $F=0.5\,s$ (hyperplane $\sum_i f_i=0.5$).
\item \textbf{convex:} $F=s^{\circ 2}$ (componentwise square. convex front
$\sum_i\sqrt{f_i}=1$).
\item \textbf{concave:} $F=d/\lVert d\rVert_2$ (concave spherical front
$\sum_i f_i^2=1$).
\item \textbf{disconnected:} the concave sphere with the first coordinate offset
by $0.6\,k$, $k\in\{0,1,2,3\}$, opening gaps between patches.
\item \textbf{degenerate:} the $s^{\circ 2}$ front with the last criterion
tied to the first ($f_m\!\leftarrow\! f_1$), giving a lower-dimensional front.
\item \textbf{asymmetric:} the concave sphere with criteria scaled by
$\mathrm{linspace}(1,5,m)$ (heterogeneous criterion ranges).
\item \textbf{many-knee:} the concave sphere warped by $F\!\mapsto\!F+0.15\sin(6F)$
to create multiple knees, then clipped to $F\ge 0$.
\item \textbf{irregular:} the concave sphere with multiplicative noise
$F\!\mapsto\!F\odot(1+0.1\,\mathcal N(0,1))$, then clipped to $F\ge 10^{-3}$ so all
criterion values stay non-negative.
\end{itemize}
All eight constructions yield non-negative criterion values (by clipping where
noted), so the subsequent active-set normalisation maps them into $[0,1]^m$.

\paragraph{Baseline specification.}
Table~\ref{tab:baselines} compactly specifies every comparator, all operating on
the active-set normalised matrix $r\in[0,1]^m$ (minimisation). $w$ denotes
equal weights $\mathbf 1/m$ unless a method samples weights.



\clearpage
