% ============================================================================
% Beyond Pareto Fronts: A Leximax Universal-Regret Core for Robust
% Multicriteria Decision Support
%
% Formatted in the standard article class for portable compilation.
% For final EJOR submission, switch the first line to
%   \documentclass[review]{elsarticle}
% and move the abstract/keywords into the elsarticle frontmatter; the body,
% theorems, tables and figures below transfer unchanged.
% ============================================================================
\documentclass[review]{elsarticle}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{pifont}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,backgrounds,shapes.geometric,shapes.arrows,calc,matrix}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\onehalfspacing

\graphicspath{{./}{./figures/}}

% ---- shared TikZ styles for the schematic figures ----
\definecolor{lexurcrimson}{HTML}{C0392B}
\definecolor{lexurslate}{HTML}{34495E}
\definecolor{lexurblue}{HTML}{2980B9}
\definecolor{lexurgreen}{HTML}{27AE60}
\tikzset{
  stage/.style={rounded corners=2pt, draw=lexurslate, line width=0.6pt,
    fill=lexurslate!6, align=center, inner sep=5pt, font=\small},
  accent/.style={rounded corners=2pt, draw=lexurblue, line width=0.7pt,
    fill=lexurblue!8, align=center, inner sep=5pt, font=\small},
  win/.style={rounded corners=2pt, draw=lexurcrimson, line width=0.9pt,
    fill=lexurcrimson!8, align=center, inner sep=5pt, font=\small},
  flow/.style={-{Stealth[length=2.4mm]}, line width=0.7pt, draw=lexurslate},
}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\reg}{D}
\newcommand{\ideal}{z^{\star}}
\newcommand{\nadir}{z^{nad}}
\newcommand{\lex}{\leq_{\mathrm{lex}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\Corr}{Corr}

\IfFileExists{generated/protocol_numbers.tex}{\input{generated/protocol_numbers.tex}}{
  \newcommand{\protocolInstances}{7,200}
  \newcommand{\protocolMethods}{11}
  \newcommand{\protocolCD}{0.178}
}

\begin{document}
\begin{frontmatter}
\title{\textbf{Lexicographic Minimax Regret over Declared Monotone Probes\\
for Robust Multicriteria Selection}}
\author{Madani Bezoui}
\address{CESI LINEACT, UR 7527}
\begin{abstract}
\noindent
Pareto efficiency is necessary but not sufficient for a unique recommendation. An
efficient set tells a decision maker (DM) which alternatives are not obviously
bad, but offers no principled way to choose one. Practice fills this gap with
\emph{post hoc} devices---weighted sums, TOPSIS, compromise programming,
reference points, acceptability indices---each injecting implicit or stochastic
preference judgements.

We propose the \textbf{Leximax Universal-Regret (LexUR) core}, a lexicographic minimax regret selection rule operating over a structured, declared, monotone scalarisation family. The
DM defines an explicit family of rational questions (probes) and supplies normalisation bounds. 
LexUR treats each probe's evaluation as an achievement function, calculating how far each alternative
falls from the best attainable outcome under each probe, and sorts the resulting
dimensionless regrets. The method returns either a singleton recommendation or, when margins or bounds are insufficient, a certified stability class, always accompanied by an interpretable certificate listing the binding questions. 

We prove existence and completeness, Pareto compatibility, stability of the
tolerance-based leximax rule under bounded perturbations, and a probe
perturbation bound with explicit constants. We also give an adaptive
correlation-clustering construction empirically reducing, without eliminating,
sensitivity to redundant criteria.

In a replicated benchmark and a broadened frozen audit protocol covering 11 methods, 10 held-out preference families, 8 front geometries, and $m$ up to 20, LexUR is competitive with robust scalarisation baselines on tail held-out loss and non-inferior to ASF and sampled minimax regret under paired tests, while a single-point hypervolume score obtains the best average rank. LexUR's distinct contributions are its labelled regret certificate and empirically reduced redundancy sensitivity relative to averaging methods. Because point-bound LexUR can be sensitive to normalisation estimates, robust deployment should report a tolerance or interval stability class; a unique recommendation is returned only when margin conditions hold. The method is robust with respect to the declared probe family, not with respect to all possible preferences. We formulate an exploratory stochastic extension illustrated on a synthetic smart-grid economic dispatch model.
\end{abstract}

\begin{keyword}
Decision support \sep Multicriteria decision analysis \sep
Robust decision making \sep Minimax regret \sep Achievement scalarising functions \sep
Pareto efficiency
\end{keyword}
\end{frontmatter}

% ---------------------------------------------------------------------------
\input{sections/01_intro}
\input{sections/02_related}
\input{sections/03_core}
\input{sections/04_direct}
\input{sections/05_probes}
\input{sections/06_extensions}
\input{sections/07_experiments}
\input{sections/08_discussion}
\input{sections/09_conclusion}

\bibliographystyle{plainnat}
\bibliography{refs}

\appendix
\input{sections/D_families}
\input{sections/B_smartgrid}
\input{sections/C_rawlsian}

\end{document}
